### 2017-05-11 paper/evaluation.tex
added aws

\begin{figure*}[t]
\centering
\small
\begin{tabular}{l|rr|rrrrrrrrrr}
\toprule
\multirow{2}{*}{\emph{Subject (module)}} & \multicolumn{2}{c|}{\emph{\Seq}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T_\text{cost} $ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%
Jankotek MapDB  & \entry{8.2m}{5324} & \entry{1.52x}{0.00\%} & \entry{2.73x}{0.00\%} & \entry{4.82x}{0.05\%}   & \entry{}{} & \entry{}{}\\%
Stripe Java     & \entry{4.3m}{302}  & \entry{4.78x}{6.31\%} & \entry{3.31x}{7.31\%} & \entry{21.50x}{14.95\%} & \entry{}{} & \entry{}{}\\%
%%OpenMRS Core (\CodeIn{api})  & \entry{15.4m}{3436} & \blankentry{}        & \blankentry{}        & \blankentry{} & \entry{1.5x}{0\%} & \entry{1.7x}{0}\\%
%%Apache Flume (\CodeIn{core}) &  \entry{7.7m}{392}  & \blankentry{}        & \blankentry{}        & \blankentry{}       & \entry{0.9x}{0\%} & \blankentry{} \\%
%%Facebook Archive Linkbench   &  \entry{4.5m}{98}   & \entry{1.0x}{0.2\%}  & \entry{1.6x}{1.2\%}       & \entry{1.0x}{0\%}  & \entry{1.7x}{0.5\%}  & \entry{1.7x}{0.2\%}\\%
%%AWS SDK Java (\CodeIn{core}) &  \entry{3.8m}{847}  & \multicolumn{6}{c}{\Fix{requires investigation}} & \entry{2.2x}{0.1\%} & \entry{3.2x}{2.0\%}\\%

>>>>

\begin{figure*}[t]
\centering
\small
\begin{tabular}{l|rr|rrrrrrrrrr}
\toprule
\multirow{2}{*}{\emph{Subject (module)}} & \multicolumn{2}{c|}{\emph{\Seq}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T_\text{cost} $ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%
Jankotek MapDB  & \entry{8.2m}{5324} & \entry{1.52x}{0.00\%} & \entry{2.73x}{0.00\%} & \entry{4.82x}{0.05\%}   & \entry{}{} & \entry{}{}\\%
Stripe Java     & \entry{4.3m}{302}  & \entry{4.78x}{6.31\%} & \entry{3.31x}{7.31\%} & \entry{21.50x}{14.95\%} & \entry{}{} & \entry{}{}\\%
AWS SDK Java (\CodeIn{core})  & \entry{3.7m}{847}  & \entry{1.95x}{2.24\%} & \entry{2.47x}{2.77\%} & \entry{3.70x}{4.01\%} & \entry{}{} & \entry{}{}\\%
%%OpenMRS Core (\CodeIn{api})  & \entry{15.4m}{3436} & \blankentry{}        & \blankentry{}        & \blankentry{} & \entry{1.5x}{0\%} & \entry{1.7x}{0}\\%
%%Apache Flume (\CodeIn{core}) &  \entry{7.7m}{392}  & \blankentry{}        & \blankentry{}        & \blankentry{}       & \entry{0.9x}{0\%} & \blankentry{} \\%
%%Facebook Archive Linkbench   &  \entry{4.5m}{98}   & \entry{1.0x}{0.2\%}  & \entry{1.6x}{1.2\%}       & \entry{1.0x}{0\%}  & \entry{1.7x}{0.5\%}  & \entry{1.7x}{0.2\%}\\%
%%AWS SDK Java (\CodeIn{core}) &  \entry{3.8m}{847}  & \multicolumn{6}{c}{\Fix{requires investigation}} & \entry{2.2x}{0.1\%} & \entry{3.2x}{2.0\%}\\%
